### 2019-08-16 index.Rmd
Update, fixed docs
Add logo

# foehnix

@@

```{r, echo = FALSE, fig = TRUE, results = 'hide', fig.width = 12, fig.height = 4}
windrose(mod, type = "histogram", mfcol = 3)
```

>>>>

# foehnix <a href='https://retostauffer.github.io/Rfoehnix/'><img src='https://github.com/retostauffer/Rfoehnix/raw/master/foehnix-logo.png' align="right" height="139" /></a>

@@

```{r, echo = FALSE, fig = TRUE, results = 'hide', fig.width = 12, fig.height = 4}
windrose(mod, type = "histogram", ncol = 3)
```
